---
title: "dsfb2_workflows_portfolio_1punt2_Measuring the evolutionarily important goals of situations: Situational Affordances for Adaptive Problems_Nick_brown"
author: "Bas Koppenaal"
date: "15-4-2021"
output: html_document
---

A: ok maar dat wordt een lange titel
B: https://journals.sagepub.com/doi/10.1177/1474704915593662
C: Yes
D: https://journals.sagepub.com/doi/10.1177/1474704915593662 
E: see list below
  Study Purpose: Good and clear
  Data Availability Statement: you can find all their data under Supplemental Material
  Data Location: yes i can use all their data and code so far as i know 
  Study Location: they give away where their study had taken place this was the Florida Atlantic University.
  Author Review: good
  Ethics Statement: yes they explain this under Participants
  Funding Statement: yes they sayed they didnt get any funding
  Code Availability: yes i can acces their code
  
f:  In Study 1 ( the study i look at), participants rated a recent situation they encountered using a preliminary version of the SAAP. Using factor analysis, the measure was reduced to 28 items. these situations are analysed using R. 
G: de naam van de folder heet: Rmarkdown_portofolio
H: https://osf.io/tcx9f/ het gaat over het artikel van hierboven. 
I: Done
J: first you open a document, than you use the code to compare the data with eachother and see if there are correlations. 
K: 4: it doesnt really work but above every part of code it says what the code should do
L: done dit heet 'study 1.R' en 'Study 1 data'
M: i got it everything running with some chances,I changed everything where it says EDIT in the line
N: i did everything where it says edit i chanced 
O: ik had in het begin wat moeite maar met een beetje hulp en wat energy ging het helemaal goed 4/5. 
P: ik vindt dit een beetje vage vraag: 

maar de code die ik aangepast heb: regel 29 - 42 


   #Load the dataset: Select Study 1 data.csv EDIT: ik heb de code hieronder vervangen door mijn eigen zodat hun document er gelijk in komt te staan. EDIT: ze gebruiken saapv met kleine en grote letters. ik verander het een beetje hier en alles groot gemaakt
## saap <- read.csv(file.choose())

SAAP <- read_excel("Lesson1/Study 1 data.xlsx")
           
           
  #Subset the dataset for valid cases , EDIT: ik heb dit ook grote letters gemaakt
##saapV <- saap[saap$Valid==1,]

SAAPV <- SAAP[SAAP$Valid==1,]

   #Check the dimension of the dataset EDIT: ik heb dit ook grote letters gemaakt
## dim(saapV)
dim(SAAPV)

regel 238 - 240

 #Choose SAAPcontent.csv  EDIT: ik snap niet precies welk bestand ze willen dat ik er nu in zet dus ik heb het eerste data bestand hier neergezet.
##SAAP.content <- read.csv(file.choose())
SAAP.content <- SAAP


regel 271 tot 277
## extra ) aan toegevoegd
#Descriptive statistics for the sample
  #Age
describe(c(SAAPV$Age))

  #Sex   EDIT: lijkt er op alsof dit de eerste keer is dat ze Sex in het stukje benoemen. ik pas het niet aan maar het geeft een error 
table(SAAPV$Sex)

https://osf.io/a2vx7/

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}


```


```{r pressure, echo=FALSE}


```
